Data for ms. 1

### 2017-05-03 ms1/ms1.Rmd
ms1

```{r p_values}
data_by_field('condition_model') %>%
  select(term, year, p.value) %>%
  mutate(adj.p=p.adjust(p.value, method='bonferroni'),
         log10.adj.p=log10(adj.p)) %>%
  filter(adj.p > 10^(-50)) %>%
  arrange(desc(log10.adj.p)) %>%
  kable
```

>>>>

```{r p_values}
data_by_field('big_model') %>%
  select(term, year, p.value) %>%
  mutate(adj.p=p.adjust(p.value, method='bonferroni'),
         log10.adj.p=log10(adj.p)) %>%
  filter(adj.p > 10^(-50)) %>%
  arrange(desc(log10.adj.p)) %>%
  kable
```
